---
title: "Bootstrap"
author: "Siquan"
date: "11/16/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
set.seed(1)
```

Generate some random samples: one case in which the usual linear regression assumptions hold and one case in which they don’t.
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source)
```

Note the above non-constant variance phenomenon above

Fit two models
```{r}
sim_df_const %>% 
  lm(y~x, data = .) %>% 
  broom::tidy()
sim_df_nonconst %>% 
  lm(y~x, data = .) %>% 
  broom::tidy()
```

## how can I bootstrap

write a function to draw a bootstrap sample based on a dataframe
```{r}
boot_sample = function(df){
  sample_frac(df, size = 1, replace = TRUE)
}

```
```{r}
boot_sample(df = sim_df_nonconst) %>% 
  ggplot(aes(x=x, y=y))+
  geom_point(alpha = 0.5)
```

Organize a dataframe
```{r}
boot_starps = 
  tibble(
    strap_num = 1:1000,
    strap_sample = rerun(1000, boot_sample(df = sim_df_nonconst))
  )
boot_starps
```

Do some kind of analysis
```{r}
bootstrap_results = 
  boot_starps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
bootstrap_results
```

## Try the modelr package
```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000)
boot_straps
boot_straps$strap[[1]]
as_data_frame(boot_straps$strap[[1]])
```

Repeat the pipeline
```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

##What if your assumption aren't wrong?
```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

If the underlying assumption is right, the results seems okay