---
title: "Data_Wrangling_1"
author: "Siquan"
date: "9/19/2019"
output: github_document
---
Tidyverse package all function in it has a df input and df output
pip %>% could help a lot --- the output of previous function will be the input of next funtion

```{r}
library(tidyverse)
#When you library tydyverse, you can see that it involves 8 packages
#Also you can see that different packages might have same function names
#filter both 
```

```{r}
litters_data = read_csv("./data_import_examples/FAS_litters.csv")
litters_data = janitor::clean_names(litters_data)
pups_data = read_csv("./data_import_examples/FAS_pups.csv")
pups_data = janitor::clean_names(pups_data)
#R only knows the dataframe overall, eg it knows litters_data this dataframe, but don't know the 'Group' column. If you want to access the group variable, you need to use pull(df, Group)
```
##The following only works on selectiong columns rather than selecting certain values
```{r}
select(litters_data,group,litter_number)#specify the columns you want to keep by naming all of them
select(litters_data,group,litter_number,gd0_weight, starts_with("pups"))
select(litters_data,group,litter_number,gd0_weight, everything())
select(litters_data,-group)#Remove the group column
select(litters_data,litter_number,gd0_weight:pups_born_alive)
#Remember that now we still don't change the original dataframe, just select sth from it. If I would like to save these changes, we should save it as a new variable
select(litters_data, GROUP = group, litter_number)#Change the name of the 'group' column
rename(litters_data, GROUP = group)#Only rename certain columns but not do the selection
```

Filtering: Works on certain values, also gives an input dataframe, and tell R how I would like to do the filtering.
```{r}
filter(litters_data, group == "Con7") #logical operator, check whether the group variable is Con7, keeps the rows when the logical operator is true.
filter(litters_data, gd_of_birth == 20)#Can also select accoridng to numerical values
filter(litters_data, gd_of_birth <20, group == "Con7")#Could have multiple logical conditions separated by comma
filter(litters_data, group == "Con7" | group == "Mod8")#Or
filter(litters_data, group %in% c("con7","Mod8"))#An equivalent way to do this--preferred sinc or(|) is a little bit difficut to debug
filter(litters_data, gd0_weight + gd18_weight < 70)
#Don;t do filter(litters_data, !is.na(gd0_weight))
drop_na(litters_data, gd0_weight)
drop_na(litters_data, gd0_weight, gd18_weight)

```
##Mutate
```{r}
mutate(litters_data, wt_gain = gd18_weight - gd0_weight,
       group = str_to_lower(group))#Could create new variables(column) and modify existing columns
```
## Arrange
```{r}
arrange(litters_data, pups_born_alive)
arrange(litters_data, desc(pups_born_alive))
arrange(litters_data, pups_born_alive,gd0_weight)
```
## pipe ...
Creating a collection of commands
```{r}
#Old-school way
litters_data_raw = read_csv("./data_import_examples/FAS_litters.csv",
  col_types = "ccddiiii")
litters_data_clean_names = janitor::clean_names(litters_data_raw)
litters_data_selected_cols = select(litters_data_clean_names, -pups_survive)
litters_data_with_vars = 
  mutate(
    litters_data_selected_cols, 
    wt_gain = gd18_weight - gd0_weight,
    group = str_to_lower(group))
litters_data_with_vars_without_missing = 
  drop_na(litters_data_with_vars, wt_gain)
litters_data_with_vars_without_missing
#A nested-approach(not suggested)---Very awful!!
litters_data_clean = 
  drop_na(
    mutate(
      select(
        janitor::clean_names(
          read_csv("./data_import_examples/FAS_litters.csv", col_types = "ccddiiii")
          ), 
      -pups_survive
      ),
    wt_gain = gd18_weight - gd0_weight,
    group = str_to_lower(group)
    ),
  wt_gain
  )

litters_data_clean
```
```{r}
#Shift + Ctrl + m will produce %>% 
litters_data = read_csv("./data_import_examples/FAS_litters.csv")%>% 
  janitor::clean_names() %>% 
  select(-pups_survive) %>% 
  mutate(
    wt_gain = gd18_weight - gd0_weight,
    group = str_to_lower(group)
  ) %>% 
  drop_na(gd0_weight)
```
```{r}
#But pip will only transfer the argument into the first argument(in tidyverse), if you want to place sth in other position, you need to clarify
litters_data %>%
  lm(wt_gain ~ pups_born_alive, data = .) %>%
  broom::tidy()###need a placeholder!!!
```

