---
title: "EDA"
author: "Siquan"
date: "10/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Set up some global criteria for all the plots you produced
```{r}
library(tidyverse)
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>% 
  mutate(
        name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10,
    month = lubridate::floor_date(date, unit = "month")) %>%
  select(name, id, date, month, everything())
```
Try group_by and summary()
```{r}
weather_df %>% 
  group_by(name, month)
```
```{r}
weather_df %>%
  group_by(month) %>%
  summarize(n = n(),
            n_unique = n_distinct(date))
```
If you just want to count, you do not need to use group_by() and summarize(), just use count()
```{r}
weather_df %>% 
  count(name,month, name = "hahaha") #You can name the count column as you want
```
Awful table() function, cannot do on df, must need to first pull it out, then use table().
Also the result is not a dataframe, you cnanot do anything else on the result of table()
```{r}
weather_df %>% 
  pull(name) %>% 
  table()
```
(Let's make a nice table)
```{r}
weather_df %>% 
  count(name) %>% 
  knitr::kable()
```
```{r}
weather_df %>% 
  filter(name != "Waikiki_HA") %>% 
  mutate(
    cold = case_when(
      tmax <5 ~ "cold",
      tmax <=5 ~ "not cold",
      TRUE ~ ""#Creat a new variable based more than two sceniros, if True, just give  ablank spot
    )
  ) %>% 
  group_by(name, cold) %>% 
  count() %>% 
  pivot_wider(
    names_from = name,
    values_from = n
  )
```
Create the 2*2 table by another function
```{r}
weather_df %>% 
  count(name) %>% 
  knitr::kable()
```
Produce a 2*2 table by changing into wide form
```{r}
weather_df %>% 
  filter(name != "Waikiki_HA") %>% 
  mutate(
    cold = case_when(
      tmax <5 ~ "cold",
      tmax <=5 ~ "not cold",
      TRUE ~ ""#Creat a new variable based more than two sceniros, if True, just give  ablank spot
    )
  ) %>% 
  janitor::tabyl(name,cold)

```
Do some general summaries
```{r}
weather_df %>% 
  group_by(name) %>% 
  summarize(
    n = n(),
    mean_tmax = mean(tmax),
    sd_tmax = sd(tmax),
    median_prcp = median(prcp)
  )
```
Have missing value, check NA
```{r}
weather_df %>% 
  filter(is.na(tmax))
```
One way to deal with NA (But not set this in default, you need to see whether there is NA in the dataset)
```{r}
weather_df %>% 
  group_by(name) %>% 
  summarize(
    n = n(),
    mean_tmax = mean(tmax,na.rm = TRUE),
    sd_tmax = sd(tmax,na.rm = TRUE),
    median_tmax = median(tmax,na.rm = TRUE)
  )
```
Create a visual summary (If you create a df by group_by() and summarize(), you can repeat what you can do on a df as previous letures)
```{r}
weather_df %>%
  group_by(name, month) %>%
  summarize(mean_tmax = mean(tmax, na.rm = TRUE)) %>%
  ggplot(aes(x = month, y = mean_tmax, color = name)) + 
    geom_point() + geom_line() + 
    theme(legend.position = "bottom")
```
```{r}
weather_df %>%
  group_by(name, month) %>%
  summarize(mean_tmax = mean(tmax, na.rm = TRUE)) %>%
  pivot_wider(
    names_from = name,
    values_from = mean_tmax
  ) %>% 
  knitr::kable(digits = 1)
```
If you group and forget about it, you will have trouble!
But you can always ungroup your df
```{r}
weather_df %>% 
  group_by(name) %>% 
  ungroup()
```
```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(
    mean_tmax = mean(tmax, na.rm = TRUE),
    centered_tmax = tmax - mean_tmax
#Now mutate will only do the mutation within groups
  ) %>% 
  ggplot(aes(x = date, y = centered_tmax, color = name)) + 
  geom_point()
```
Window function in grouped mutates
```{r}
weather_df %>% group_by(name,month) %>% 
  mutate(
    temp_ranking = min_rank(tmax)
  ) %>%
  filter(temp_ranking == 1) #This window function is useful when doing filtering afterwards
#Find the coldest daten within each group
```
```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(
    lagged_tmax = lag(tmax),
    one_day_tmax_change = tmax - lagged_tmax
  ) %>% 
  summarize(sd_daily_change = sd(one_day_tmax_change, na.rm = TRUE))
```
Mutate is to change the df (like adding a new column or something), but summarize() is just gives u some summary statistics

##lag() function only works with the long formate

group_by() only works within the code chunk if you do not save it

