---
title: "ggplot1"
author: "Siquan"
date: "9/26/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

```{r load_data, cache = TRUE}
#Load data from R packages in weather monitoring(rnoaa is a packages that conatins the weather information)
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```
#Create a ggplot
```{r}
ggplot(weather_df,aes(x=tmin, y=tmax))+
  geom_point()#First element is the dataset, second element is the mapping(what ging to be the x-aes and y-aes, the third element is what kind of graph it should make)
```
Altenrtaive way to make this plot
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()
```
Save initial plots
```{r}
scatterplot = weather_df %>%
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()
scatterplot
```
Adding color
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))+
  geom_point(aes(color = name),alpha = 0.5)#Put a color aes in the plot
```
Why do 'aes' positions matter?
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))+ #Define static mapping everywhere in my ggplot
  geom_point(aes(color = name),alpha = 0.5)+#Color matters only in geom_point, but does not matter in geom_smooth()
  geom_smooth()#Put a color aes in the plot
```
If we change, now color as a static mapping everywhere in my plot. color now apply everywhere in my plot. 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+ #Define static mapping everywhere in my ggplot
  geom_point(alpha = 0.5)+
  geom_smooth()#Put a color aes in the plot
```
Facet!
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+ #Define static mapping everywhere in my ggplot
  geom_point(alpha = 0.5)+
  geom_smooth()+
  facet_grid(.~name)
#Separate by name, gives you subplots
```
This is fine, but not interesting
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name))+
  geom_point(aes(size = prcp), alpha = 0.4)+
  geom_smooth(size = 1.5)
```
## Some extre staff
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name))+
  geom_smooth(size = 1.5)
#geom_point() is not a must, just vanish the individual points
```
#2D density
```{r}
library(hexbin)
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_hex()
```
#More kinds of plots!
```{r}
weather_df %>% 
  ggplot(aes(x = tmax,fill = name))+
  geom_histogram(position = "dodge")
#Histogram does not need to specify the y-aex---only cares about counts
```
Density Plots
```{r}
weather_df %>% 
  ggplot(aes(x = tmax,fill = name))+
  geom_density(alpha = 0.3)
#I really like density plot!(Since it is more smooth)
```
#Some other univariate plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax))+
  geom_boxplot()
#Box plots are really great!
```
#Violin Plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax))+
  geom_violin()
```
#Ridge Plots
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
#Could compare the distributions
```
The reason why ggplot use '+' because pip is invented after the invention of ggplot. 

Saving a plot!
Don;t use the export button since it is not reproducible!!
```{r}
ggp_ridge_temp = ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
ggsave("ggplot_tem_ridge.pdf", ggp_ridge_temp)#If you don't specify the plot that you wnat to save, ggplot will automatically save the last plot you produce
```
#Embedding plots in R markdown
The difficulty is that the font and point size in the figures generated by R are constant – that is, they don’t scale with the overall size of the figure. As a result, text in a figure with width 12 will look smaller than text in a figure with width 6 after both have been embedded in a document
```{r, fig.width = 12}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```
```{r, fig.width = 6}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```
You should keep an eye on it!
Could use width. height command in your code!