---
title: "ggplot2"
author: "Siquan"
date: "10/01/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(patchwork)
```

```{r load_data, cache = TRUE}
#Load data from R packages in weather monitoring(rnoaa is a packages that conatins the weather information)
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```
Star twith an old plot
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)
```
Adding labels:
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)+
  labs(
    title = "Temperature Plot",
    x = "Minimum Temp (X)",
    y = "Minimum Temp (Y)",
    caption = "Data from NOAA via rnoaa package"
  )
```
X axis acale
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)+
  labs(
    title = "Temperature Plot",
    x = "Minimum Temp (X)",
    y = "Minimum Temp (Y)",
    caption = "Data from NOAA via rnoaa package"
  )+
  scale_x_continuous(
    breaks = c(-15, -5, 20), 
    labels = c("-15C","-5","20")
  )
#The plots has the specific tickmarks as I set
```
Get some transformation
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)+
  labs(
    title = "Temperature Plot",
    x = "Minimum Temp (X)",
    y = "Minimum Temp (Y)",
    caption = "Data from NOAA via rnoaa package"
  )+
  scale_x_continuous(
    breaks = c(-15, -5, 20), 
    labels = c("-15C","-5","20"),
  )+
  scale_y_continuous(
      trans = "sqrt"
    )
```
One drawback is that ggplot has multiple arguments to do the same thing so that just use the first asnwer you get on the stackoverflow


#Change colors
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)+
  labs(
    title = "Temperature Plot",
    x = "Minimum Temp (X)",
    y = "Minimum Temp (Y)",
    caption = "Data from NOAA via rnoaa package"
  )+
  scale_color_hue(
    name = "Location",
    h = c(100,2000)
  )#Have many acale-color color options, but encourgae you not to do that
```
#See the viridis color package --- get more color
```{r}
ggp_base = weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name))+
  geom_point(alpha = 0.5)+
  labs(
    title = "Temperature Plot",
    x = "Minimum Temp (X)",
    y = "Minimum Temp (Y)",
    caption = "Data from NOAA via rnoaa package"
  )+
  viridis::scale_color_viridis(
    name = "Location",
    discrete = TRUE
  )#Now the color are more separateble
```
Now we discuss with theme, the overall theme of your plot
```{r}
ggp_base+
  theme(legend.position = "bottom")
```
```{r}
ggp_base+
  theme(legend.position = "none")
```
#In ggplot theme, the order matters
```{r}
ggp_base+
  theme_minimal()+
  theme(legend.position = "bottom")
```
```{r}
ggp_base+
  theme(legend.position = "bottom")+
  theme_minimal()
#These two ways are different
```
#Set some global graph settings to all the plots that will be generated
```{r}
# More than one dataset
central_park = 
  weather_df %>% 
  filter(name == "CentralPark_NY")

waikiki = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(data = waikiki, aes(x = date, y = tmax, color = name)) + 
  geom_point() + 
  geom_line(data = central_park)
```
(brief aside about colors)
```{r}
waikiki %>% 
  ggplot(aes(x = date, y = tmax, color = name))+
  geom_point()
```
```{r}
waikiki %>% 
  ggplot(aes(x = date, y = tmax))+
  geom_point(color = "blue")
```
#Multi-panel plots
```{r}
devtools::install_github("https://github.com/thomasp85/patchwork")
```

```{r}
ggp_scatter = 
  weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))+
  geom_point()

ggp_density =
  weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))+
  geom_density()

ggp_box =
  weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))+
  geom_boxplot()
  
```
Sometimes the order of catogirical variables are determnined by alpabetical order, but this might not be what we want, so we need to reorder them manually.
```{r}
weather_df %>% 
  mutate(
    name = factor(name),
    name = fct_reorder(name, tmax)
  )%>% 
  ggplot(aes(x=tmax, y=name))+
  geom_point()
```
#To make some more complicated graph, may need to do some more tidy on data first
```{r}
weather_df %>% 
  pivot_longer(
    tmax:tmin,
    names_to = "observation",
    values_to = "temperature"
  ) %>% 
  ggplot(aes(x= temperature, fill = observation))+
  geom_density() +
  facet_grid(~name)
```
```{r}
pup_data = 
  read_csv("./data/FAS_pups.csv", col_types = "ciiiii") %>%
  janitor::clean_names() %>%
  mutate(sex = recode(sex, `1` = "male", `2` = "female")) 

litter_data = 
  read_csv("./data/FAS_litters.csv", col_types = "ccddiiii") %>%
  janitor::clean_names() %>%
  select(-pups_survive) %>%
  separate(group, into = c("dose", "day_of_tx"), sep = 3) %>%
  mutate(wt_gain = gd18_weight - gd0_weight,
         day_of_tx = as.numeric(day_of_tx))

fas_data = left_join(pup_data, litter_data, by = "litter_number") 

fas_data %>% 
  select(sex, dose, day_of_tx, pd_ears:pd_walk) %>% 
  pivot_longer(
    pd_ears:pd_walk,
    names_to = "outcome", 
    values_to = "pn_day") %>% 
  drop_na() %>% 
  mutate(outcome = forcats::fct_reorder(outcome, day_of_tx, median)) %>% 
  ggplot(aes(x = dose, y = pn_day)) + 
  geom_violin() + 
  facet_grid(day_of_tx ~ outcome)
```








