---
title: "Untitled"
author: "Siquan"
date: "11/1/2019"
output: github_document
---

List is very general data structure in R, could contain anything!

Learn how to use map() to replace for loops
```{r}
library(tidyverse)

set.seed(1)
```

```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l
```
Play with lists
```{r}
l$summary
l$vec_numeric
l$vec_logical
l[[1]][1:3]
```

Data frame is just a list
```{r}
df = list(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)
df
df$a
df[[2]]
```
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

Still copy and paste the same code several times
```{r}
```


```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])

```

Try to iterate over the things that we are interested in!
First create sth to store the output!

```{r}
output = vector("list", length = 4)
```

Write our first for loop!

```{r}
for ( i in 1:4){
  output[[i]] = mean_and_sd(df[[i]])
}
```

Change the for loop to a map statement--When you use map(), you donnot need to make sth to store the result, you can directly assign it to some variable! 

```{r}
output = map(df, mean_and_sd)
output_median = map(df, median)

output_median = map_dbl(df,median)
output = map_dfr(df, mean_and_sd)
```

Some syntax you can use when using map()--Being more explicit and saying what things we are going to work on 

```{r}
output = map(df, ~mean_and_sd(.x))
```

get all the pages!
```{r}
library(rvest)

read_page_reviews = function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```

Crete a vector of url that I would like to work on 

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

The following code is tidious
```{r}
read_page_reviews((vec_urls[[1]]))
read_page_reviews((vec_urls[[2]]))
read_page_reviews((vec_urls[[3]]))
read_page_reviews((vec_urls[[4]]))
read_page_reviews((vec_urls[[5]]))

```
 Write a for loop!
 
```{r}
output = vector("list", length =5)
for (i in 1:5){
  output[[i]] =read_page_reviews((vec_urls[[i]]))
}
output
```
 
 Use map()
 
```{r}
output = map(vec_urls, read_page_reviews)
```

List columns!

```{r}
weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2016-01-01",
    date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

nest within station

```{r}
weather_nest =weather %>% 
  nest(data = date:tmin)
```

Is the list column really a list?

A list of list, with length eqaul to the other entries-- we have another column and call it list column!

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)
weather_nest$data[[1]]
```

#Operations on list columns

Can I do things with a list column?
```{r}
central_park_df = weather_nest$data[[1]]
lm(tmax~tmin, data = central_park_df)
lm(tmax~tmin, data = weather_nest$data [[2]])
lm(tmax~tmin, data = weather_nest$data [[3]])
```

Try a loop
```{r}
output = vector ("list", length =3)
for ( i in 1:3){
  output[[i]] = lm(tmax~tmin, data = weather_nest$data[[i]])
}
```

```{r}
weather_lm = function(df){
  lm(tmax~tmin, data =df)
}
```

List column has very powerful functions like following: (using map())
```{r}
for (i in 1:3){
  output[[i]]=weather_lm(weather_nest$data[[i]])
}
output = map(weather_nest$data, weather_lm)
```

Very interesting operation on nested lists!
```{r}
weather_nest %>% 
  mutate(lin_models = map(data, weather_lm))
```

#Revisit napolean..again

```{r}
dynamite_reviews = 
  tibble(page = 1:5,
         urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()

lotr_cell_ranges = 
  tibble(
    movie = c("fellowship_ring", "two_towers", "return_king"),
    cells = c("B3:D6", "F3:H6", "J3:L6")
  )

```

