---
title: "String_Factor"
author: "Siquan"
date: "10/15/2019"
output: github_document
---

Factors have underlying structure! numerical structure! Categorical Structual!
Read.csv() will automatically make the strings as factors, but sometime it is uncessary!
Strings and regular expression!--when you only know a general form but know the exact form
```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)
#Tidyverse has the default package for dealing with string and factor
```
Tidyverse package always deals with a data.frame
```{r}
string_vector = c("I", "love","biostatistics")
str_detect(string_vector, "love")#Every function you would like to use in the stringr package wil start with str_
str_detect(string_vector, "lo")#Not for exact string, could also detect pattern
str_detect(string_vector, "o")
```
```{r}
str_replace(string_vector, "love", "LOVE")
str_replace(string_vector, "o", "O")#Everywhere it shows up, it will replace it 
```
For exact matches, you can designate matches at the beginning or end of a line---Like regular expression
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )
str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")#Things start with i think
str_detect(string_vec,"i think$")#Things ends with i think
```
[] gives you a range of possibilities you would like to match
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )
str_detect(string_vec, "[Bb]ush")
```
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```
. matches anything
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```
Things get wired if you have some special symbols
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

Deal with real data!
```{r}
pulse_data = 
  haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit", 
    names_prefix = "bdi_score_",
    values_to = "bdi") %>%
  select(id, visit, everything()) %>%
  mutate(
    visit = str_replace(visit, "bl", "00m"),
    visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)
print(pulse_data, n = 12)
```

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

table_marj = 
  read_html(nsduh_url) %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>%
  html_table() %>%
  slice(-1) %>%
  as_tibble()
```
Question about Mutate!
```{r}
table_marj %>% 
  select(-contains("P Value")) %>% #Contains work with regular expression
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to = "percent"
  ) %>% 
  separate(age_year, into = c("age","year"),sep = "\\(") %>% 
  mutate(
  year = str_replace(year, "\\)", ""),
  percent = str_replace(percent, "[a-c]$", ""),
  percent = as.numeric(percent)
  ) %>% 
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```
```{r}
table_marj %>% 
  select(-contains("P Value")) %>% #Contains work with regular expression
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to = "percent"
  ) %>% 
  separate(age_year, into = c("age","year"),sep = "\\(") %>% 
  mutate(
  year = str_replace(year, "\\)", ""),
  precent = str_replace(percent, "[a-c]$", "777")
  ) %>% 
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```


One trouble of factor is that if you only look at labels, you may think they are same. But if you look at underlying staurctures, it might be different.
```{r}
vec_sex = factor(c("male", "male", "female", "female"))
vec_sex
```

```{r}
as.numeric(vec_sex)
```
```{r}
vec_sex = relevel(vec_sex, ref = "male")
vec_sex
```
Looks same but the numerical value has been changed!
```{r}
as.numeric(vec_sex)
```
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
```{r}
weather_df %>%
  mutate(name = forcats::fct_relevel(name, c("Waikiki_HA", "CentralPark_NY", "Waterhole_WA"))) %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```
Restaurant Data
```{r}
data("rest_inspec")

rest_inspec %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```

```{r}
rest_inspec =
  rest_inspec %>%
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  mutate(boro = str_to_title(boro))
```

```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```
ggplot set the fACTOr level by alphabetical order
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() 
```
Tell ggplot how to order the factors
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(boro = fct_infreq(boro)) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() 
```
Suppose I want to rename a boro; I’ll try to do this using replace. --- DO THIS WILL CAUSE ERROR

rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(
    boro = fct_infreq(boro),
    boro = replace(boro, which(boro == "Brooklyn"), "HipsterHQ")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)

Try this. 
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(
    boro = fct_infreq(boro),
    boro = str_replace(boro, "Brooklyn", "HipsterHQ")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() 
```
It works in some sense, but it changes it to be a string...

Finally use this!
```{r}
library("viridis")
rest_inspec %>% 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) %>%
  mutate(
    boro = fct_infreq(boro),
    boro = fct_recode(boro, "HipsterHQ" = "Brooklyn")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)
```

