---
title: "Writing Functions"
author: "Siquan"
date: "10/27/2019"
output: github_document
---

#How to make your code more efficient, especially when you need to do same thing for more than one time---write a function!

#Generally you don't make your function to use stuff in your global environmet (everytime you call a function, it creats a local environment)

```{r}
library(tidyverse)
library(rvest)
```
#Get started
Do some variable standardization
```{r}
x = rnorm(n=30, mean = 4, sd =2.3)
x_again = rnorm(n=30, mean =6, sd =3)
(x-mean(x))/sd(x)
(x_again-mean(x_again))/sd(x_again)
```
Now a function
```{r}
z_score = function(input_x){
  
  if (!is.numeric(input_x)){
    stop("Argument x should be numeric")
  }else if (length(input_x) <=3){
    stop("X should be longer")
  }
  list(
  mean_input = mean(input_x),
  sd_input = sd(input_x),
  z_score = (input_x-mean(input_x))/sd(input_x)
  )

}
```
List could let you combine everything you would like to combine into R structure

Try out the function
```{r}
z_score(input_x=x)
```
#Let's look at multiple inputs
```{r}
sim_regression = function(n, beta0, beta1){
  
  sim_data = tibble(
    x = rnorm(n, mean =1, sd =1),
    y = beta0+beta1*x+rnorm(n,mean=0, sd=1)
  )
  
  ls_fit = lm(y~x, data = sim_data)
  
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

```{r}
sim_regression(100,2,3)
```
#Script Amazon
Here is the code we write before to get the information about review on Amazon
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()
review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()
review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

```{r}
read_page_reviews = function(page_url) {
  
  dynamite_html = read_html(page_url)
  review_titles = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
    
}
```

```{r}
read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")
```
#Pass a function into the argument of another function
```{r}
x =rnorm(25,0,1)
my_summary = function(x,summ_function){
  summ_function(x)
}
my_summary(x, mean)
```

#Scope of variables
```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```


